---
title: "Appendix for Part1"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
pilot survey to determine n (our sample size) 
```{r}
set.seed(2023)
sample(1:1243,10,replace = F)
```

So our pilot survey house numbers are shown above.
We will use Y to denote number of people lived in a house  
X to denote the summation of wealth of people lived in a house
```{r}
pilot<-read.csv("pilot.csv")
Y_pilot<-pilot$population
X_pilot<-pilot$wealth
#Let v denote the pre-sample estimate for sigma
v_Y<-var(Y_pilot)
v_X<-var(X_pilot)
N<-1229
alpha<-0.05
d1<-0.4; d2<-450; d3<-2000; d4<-2500000
zsqaure<-qnorm(0.975)*qnorm(0.975) 
n1<-1/(1/N+d1^2/(v_Y*zsqaure)*(1-1/N)) 
n2<-1/(1/N+d2^2/(N^2*v_Y*zsqaure)*(1-1/N)) 
n3<-1/(1/N+d3^2/(v_X*zsqaure)*(1-1/N))
n4<-1/(1/N+d4^2/(N^2*v_X*zsqaure)*(1-1/N)) 
n1;n2;n3;n4
n<-85 #our sample size
```
sample from the houses  
```{r}
set.seed(3011)
survey<-sample(1:1229,n)
survey
```

find the sample means and their variance

```{r}
library(ggplot2)
sampledata<-read.csv("sampledata.csv")
sampledata
Y<-sampledata$population
#put the number of people lived in the house of our sample into Y
X<-sampledata$wealth
#put the summation of wealth of people lived in a house of our sample into X
max(Y); min(Y)
yv<-NULL
for (i in 0:7)  yv<-c(yv,length(Y[Y==i]) )
max(X); min(X)
xv<-NULL
for (i in 0:11)  xv<-c(xv,length(X[X>=(2000*i) & X<=(2000*(i+1))]) )
dfy=data.frame(Population=seq(0:7),count=yv)
par(mfrow=c(2,2))
ggplot(data=dfy,mapping = aes(x=Population,y=count))+geom_bar(stat = "identity")
ggplot(data=sampledata,mapping = aes(x=wealth))+geom_histogram(bins = 11)
qqnorm(Y)
qqline(Y, col="blue")
qqnorm(X)
qqline(X, col="blue")
Y_bar<-mean(Y)
Y_bar; var(Y)
var_Y_bar<-(1-n/N)*var(Y)/n
var_Y_bar
X_bar<-mean(X)
X_bar; var(X)
var_X_bar<-(1-n/N)*var(X)/n
var_X_bar
```

use the above values to calculate the estimator of total population and total wealth and their corresponding variance  
let tau_Y denote the total population  
let tau_X denote the total wealth
```{r}
tau_Y_head<-N*Y_bar
tau_Y_head
var_tau_Y_head<-N^2*(1-n/N)*var(Y)/n
var_tau_Y_head
#CI for total population 
tau_Y_head+qnorm(0.975)*sqrt(var_tau_Y_head)
tau_Y_head-qnorm(0.975)*sqrt(var_tau_Y_head)
tau_X_head<-N*X_bar
tau_X_head
var_tau_X_head<-N^2*(1-n/N)*var(X)/n
var_tau_X_head
#CI for total wealth
tau_X_head+qnorm(0.975)*sqrt(var_tau_X_head)
tau_X_head-qnorm(0.975)*sqrt(var_tau_X_head)
```






